An Approach to Off-line Handwriting Recognition through Segmentation Techniques and Deep Neural Networks

### 2017-12-17 Report/paper.tex
done

\subsection{Oversegmentation correction}
In this section we provide techniques to verify the correctness of segmentation points.
\cite{evalsplitpoints} discusses three approaches to evaluate segmentation point correctness: rule based techniques, cost function optimization based methods and machine learning based procedures.
In this paper we discuss machine learning based approaches precedented by a few rule based techniques.

@@

More rule based filter could be added for more optimal processing of the potential segmentation points.
However the focus of our segmentation correction is the neural network used to remove incorrect segmenatation points.

@@

The text to word segmentation process can be improved upon and made more robust.
More advanced text segmentation approaches can be utilized to extract the text segments from documents containing images and other unwanted elements. \cite{textsegm}
Algorithms that provide better noise reduction can be added to handle text images with more noise,
and experiments with rotations of the text can provide us with a more robust system to tackle text images containing heavily slanted text lines.

The character segmentation process is insufficient as it is, and generally unable to segment words adequately so that the character recognition step can recognise the found segments.
More postprocessing can be used through rule based techniques and a more robust neural network to correct the found segmentation points. \cite{segmtechniques}

>>>>

\subsection{Oversegmentation correction}
In this section we provide techniques to verify the correctness of segmentation points.
\cite{evalsplitpoints} discusses three approaches to evaluate segmentation point correctness: rule-based techniques, cost function optimization based methods and machine learning based procedures.
In this paper we discuss machine learning based approaches precedented by a few rule-based techniques.

@@

More rule-based filter could be added for more optimal processing of the potential segmentation points.
However the focus of our segmentation correction is the neural network used to remove incorrect segmenatation points.

@@

The text to word segmentation process can be improved upon and made more robust.
More advanced text segmentation approaches can be utilized to extract the text segments from documents containing images and other unwanted elements. A comparison of different text segmentation techniques is done by \cite{textsegm}.

The character segmentation process is insufficient as it is, and generally unable to segment words adequately so that the character recognition step can recognise the found segments.
More postprocessing can be used through rule-based techniques and a more robust neural network to correct the found segmentation points.
Several rule-based techniques are proposed by \cite{segmtechniques}.
